LSOA domestic Electricty and Gas maps

### 2021-09-21 LSOA domestic Elec and Gas.Rmd
added fig width to test

### Plotting over 65s against dom elec consumption 
```{r Loading in the Census age data}
inFile<-paste0(dataFolder, "census/KS102EW-age-categories.csv")
census_age<-readr::read_csv (inFile)
census_age$'LSOA11CD'<- census_age$'geography code'
census_age$prop_65m <- census_age$`Over 65s`/census_age$`Age: All usual residents; measures: Value`
head(census_age)
names(census_age)
message("Original Proportion Over 65:")
summary(census_age$`Proportion Over 65`)
message("New prop_65m:")
summary(census_age$prop_65m)
```
```{r Plotting elec consumption in the over 65s}
#BROKEN
#domelec_LSOA_2019$LSOA11CD <-domelec_LSOA_2019$`Local Authority Name`
#census_age_2019elec <- merge(domelec_LSOA_2019, census_age, by= "LSOA11CD")
#head(census_age_2019elec)
#Select varibale we want
#aggec_2019 <- dplyr::select(census_age_2019elec, LSOA11CD, "Local Authority Name", "Proportion Over 65", mean_de2019, prop_65m )
#head(aggec_2019)
domelec_LSOA_2019$LSOA11CD <- domelec_LSOA_2019$`Lower Layer Super Output Area (LSOA) Code`
Census_age_elec2019 <- merge(domelec_LSOA_2019, census_age, by = "LSOA11CD")
# select the variables we want for clarity

@@

```{r ageOACAndElec}

# you'll need this data (on sharepoint)
oac_df <- readr::read_csv(paste0(dataFolder, "oac/lsoa-oac-data.csv"))

@@

# plotting the gas consumption of Winchester in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill = mean_dg2019)) +
  scale_fill_continuous(name = "Gas: Mean kWh per meter", low = "green", high = "red") +
  labs(caption = "Winchester")
```
### Plotting gas usage against proportion of over 65s
```{r Loading in the Census age data}
inFile<-paste0(dataFolder, "census/KS102EW-age-categories.csv")
census_age<-readr::read_csv (inFile)
census_age$'LSOA11CD'<- census_age$'geography code'
census_age$prop_65m <- census_age$`Over 65s`/census_age$`Age: All usual residents; measures: Value`
head(census_age)
names(census_age)
message("Original Proportion Over 65:")
summary(census_age$`Proportion Over 65`)
message("New prop_65m:")
summary(census_age$prop_65m)
```
```{r Plotting gas consumption in the over 65s}
domelec_LSOA_2019$LSOA11CD <- domelec_LSOA_2019$`Lower Layer Super Output Area (LSOA) Code`
Census_age_elec2019 <- merge(domelec_LSOA_2019, census_age, by = "LSOA11CD")
# select the variables we want for clarity

>>>>

### Plotting over 65s against dom elec consumption

```{r Loading in the Census age data}
inFile<-paste0(dataFolder, "census/KS102EW-age-categories.csv")
census_age<-readr::read_csv (inFile)
census_age$'LSOA11CD'<- census_age$'geography code'
census_age$prop_65m <- census_age$`Over 65s`/census_age$`Age: All usual residents; measures: Value`
head(census_age)
names(census_age)
message("Original Proportion Over 65:")
summary(census_age$`Proportion Over 65`)
message("New prop_65m:")
summary(census_age$prop_65m)
```

```{r Plotting elec consumption in the over 65s}
#BROKEN
#domelec_LSOA_2019$LSOA11CD <-domelec_LSOA_2019$`Local Authority Name`
#census_age_2019elec <- merge(domelec_LSOA_2019, census_age, by= "LSOA11CD")
#head(census_age_2019elec)
#Select varibale we want
#aggec_2019 <- dplyr::select(census_age_2019elec, LSOA11CD, "Local Authority Name", "Proportion Over 65", mean_de2019, prop_65m )
#head(aggec_2019)
domelec_LSOA_2019$LSOA11CD <- domelec_LSOA_2019$`Lower Layer Super Output Area (LSOA) Code`
Census_age_elec2019 <- merge(domelec_LSOA_2019, census_age, by = "LSOA11CD")
# select the variables we want for clarity

@@

```{r ageOACAndElec, fig.width=6}
# you'll need this data (on sharepoint)
oac_df <- readr::read_csv(paste0(dataFolder, "oac/lsoa-oac-data.csv"))

@@

# plotting the gas consumption of Winchester in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill = mean_dg2019)) +
  scale_fill_continuous(name = "Gas: Mean kWh per meter", low = "green", high = "red") +
  labs(caption = "Winchester")
```
### Plotting gas usage against proportion of over 65s

```{r Plotting gas consumption in the over 65s}
domelec_LSOA_2019$LSOA11CD <- domelec_LSOA_2019$`Lower Layer Super Output Area (LSOA) Code`
Census_age_elec2019 <- merge(domelec_LSOA_2019, census_age, by = "LSOA11CD")
# select the variables we want for clarity
